\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-24 k-planar.tex
Deleted note

\begin{proof}
\note{PM}{I fixed some issues here that come from the fact that some vertices of $G_0$ do not contribute faces to $G_1$.  This happens when two nations and two lakes meet at a vertex $x$.  It's not an issue but it means we can't write ``the face of $G_1$ that corresponds to $x$.''}
Let $G_0$ be a graph embedded in the plane, with each face labelled a nation or a face, and where each vertex of $G_0$ is incident with at most $d$ nations. If two lakes have a common edge in their boundaries, then we may delete the edges and merge the lakes. Now assume that no two lakes have a common edge in their boundaries.
Let $G$ be the corresponding map graph.
Let $G_1$ be the graph with $V(G_1):=V(G)$, which is the set of nations, and whose edge set we now define.  Consider vertices $v$ and $w$ of $G_1$.
Let $A$ and $B$ be the nation faces of $G_0$ corresponding to $v$ and $w$.
Then $vw\in E(G_1)$ if $A$ and $B$ have a common edge in their boundaries,
or there is a vertex $x$ of $G_0$ in the boundary of $A$ and $B$, and in the clockwise or anticlockwise order of faces around $x$, all the faces between $A$ and $B$ are lakes.
% Then $G_1$ has Euler genus at most $g$.
Each face of $G_1$ corresponds to a vertex of $G_0$ or a lake of $G_0$.
Triangulate each face of $G_1$ corresponding to a lake of $G_0$.

>>>>

\begin{proof}
% \note{PM}{I fixed some issues here that come from the fact that some vertices of $G_0$ do not contribute faces to $G_1$.  This happens when two nations and two lakes meet at a vertex $x$.  It's not an issue but it means we can't write ``the face of $G_1$ that corresponds to $x$.''}
Let $G_0$ be a graph embedded in the plane, with each face labelled a nation or a face, and where each vertex of $G_0$ is incident with at most $d$ nations. If two lakes have a common edge in their boundaries, then we may delete the edges and merge the lakes. Now assume that no two lakes have a common edge in their boundaries.
Let $G$ be the corresponding map graph.
Let $G_1$ be the graph with $V(G_1):=V(G)$, which is the set of nations, and whose edge set we now define.  Consider vertices $v$ and $w$ of $G_1$.
Let $A$ and $B$ be the nation faces of $G_0$ corresponding to $v$ and $w$.
Then $vw\in E(G_1)$ if $A$ and $B$ have a common edge in their boundaries,
or there is a vertex $x$ of $G_0$ in the boundary of $A$ and $B$, and in the clockwise or anticlockwise order of faces around $x$, all the faces between $A$ and $B$ are lakes.
% Then $G_1$ has Euler genus at most $g$.
Each face of $G_1$ corresponds to a vertex of $G_0$ or a lake of $G_0$.
Triangulate each face of $G_1$ corresponding to a lake of $G_0$.
